### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@7e00940b0c342f4a700a0ca036ad502368be0f0d 🚀

@@

In order to examine how MCC, \(F_1\), \(\kappa\), and informedness
change w.r.t. the imbalance, skill, and bias, we performed a grid
exploration of the values of \(\text{logit}(s)\) and \(\text{logit}(b)\)
linearly from \(-10\) to \(10\), of \(\rho\) linearly in \(]0, 0.5]\),
which is within the range of usually observed connectance values for
empirical food webs. Note that at this point, there is no food web model
to speak of; rather, the confusion matrix we discuss can be obtained for
any classification task.

@@

\hypertarget{are-the-measures-affected-by-connectance}{%
\subsection{Are the measures affected by
connectance?}\label{are-the-measures-affected-by-connectance}}

>>>>

\hypertarget{definition-of-the-performance-measures}{%
\subsection{Definition of the performance
measures}\label{definition-of-the-performance-measures}}

\(\kappa\)

\(F_{\beta}\)

informedness

MCC

@@

In order to examine how MCC, \(F_1\), \(\kappa\), and informedness
change w.r.t. the imbalance, skill, and bias, we performed a grid
exploration of the values of \(\text{logit}(s)\) and \(\text{logit}(b)\)
linearly from \(-10\) to \(10\), of \(\rho\) linearly in \(]0, 0.5]\),
which is within the range of usually observed connectance values for
empirical food webs. Note that at this point, there is no food web model
to speak of; rather, the confusion matrix we discuss can be obtained for
any classification task. Based on the previous discussion, the desirable
properties for a measure of classifier success should be: an increase
with classifier skill, especially at low bias; a hump-shaped response to
bias, especially at high skill, and ideally center around
\(\text{logit}(b)=0\); an increase with prevalence up until
equiprevalence is reached.

@@

In fig.~\ref{fig:bias}, we show that none of the four measures satisfy
all the considerations at once: \(F_1\) increases with skill, and
increases monotonously with bias; this is because \(F_1\) does not
account for true negatives, and the increase in positive detection masks
the over-prediction of interactions. Informedness varies with skill,
reaching 0 for a no-skill classifier, but is entirely unsensitive to
bias. Both MCC and \(\kappa\) have the same behavior, whereby they
increase with skill. \(\kappa\) peaks at increasing values of biass for
increasing skill, \emph{i.e.} is likely to lead to the selection of a
classifier that over-predicts interactions. By contract, MCC peaks at
the same value, regardless of skill, but this value is not
\(\text{logit}(b)=0\): unless at very high classifier skill, MCC risks
leading to a model that over-predicts interactions. In
fig.~\ref{fig:connectance}, we show that all measures except \(F_1\)
give a value of 0 for a no-skill classifier, and are forced towars their
correct maximal value when skill changes (\emph{i.e.} a more connected
networks will have higher values for a skilled classifierd, and lower
values for a classifier making mostly mistakes).
